Using change scores

### 2024-06-20 text/22/analysis-of-means.Rmd
Update 2022 files

---
title: "A simple visual alternative to all pairwise comparisons"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
---

>>>>

---
title: "A simple visual alternative to all pairwise comparisons"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
page_update: complete
---

### 2024-06-20 text/22/baseline-covariate.Rmd
Update 2022 files

---
title: "Using change scores"
author: "Steve Simon"
source: new
date: "2022-02-01"
category: 
- Blog post
tags:
- Analysis of covariance
- Incomplete page
output: html_document
---

>>>>

---
title: "Using change scores"
author: "Steve Simon"
source: new
date: "2022-02-01"
category: 
- Blog post
tags:
- Analysis of covariance
- Incomplete page
output: html_document
page_update: complete
---
